\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{scrextend}

%\usepackage{showframe} % debugging use only

\geometry{
  letterpaper,
  left = 0.5in,
  right = 0.5in,
  top = 0.6in,
  bottom = 0.6in
}

\hypersetup{
  colorlinks = true, 
  linkcolor = blue, 
  urlcolor  = blue,
  citecolor = blue, 
  anchorcolor = blue
}

%   CUSTOM STYLES  %
\thispagestyle{empty} % remove page number
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%   MACROS  %
\newcommand{\sectionStart}{
  \begin{itemize}[label={},leftmargin=0in]
}
\newcommand{\sectionEnd}{
  \end{itemize}
}
\newcommand{\head}[9]{
  \noindent
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \centerline{
      \textbf{\href{#1}{\color{black}{\LARGE {\underline{#2}}}}}
    }
    \vspace{5pt}\\
    \centerline{
      \href{mailto:#3}{\underline{#3}} $\mid$
      #4 $\mid$
      #5 : \href{#6}{\underline{#7}} $\mid$
      #8 : \href{#9}{\underline{#7}}
    }
  \end{tabular*}
  \vspace{-10pt}
}
\newcommand{\summaryText}[1]{
  \item
  \begin{addmargin}[7pt]{0pt}
    {#1}
  \end{addmargin}
}
\newcommand{\educationItem}[5]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r@{}}
    {#1 in \textbf{#2}}  & {#3}\\
    {\textit{#4}} & {#5}\\\vspace{-18pt}
  \end{tabular*}
  \vspace{-5pt}
}
\newcommand{\skillItem}[2]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{}l@{}}
    {\textbf{#1}: } & {#2}
  \end{tabular*}\vspace{-17pt}
}
\newcommand{\jobHeading}[3]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{\textbf{#1}} & #2 \\
    \textit{\small#3} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\projectHeading}[4]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{{\href{#1}{#2}} \textbf{#3}} & #4 \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\listStart}{\begin{itemize}}
\newcommand{\listEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\bulletItem}[1]{
  \item
  \small{
    {#1 \vspace{-1.8pt}}
  }
}

\begin{document}

%   HERO   %
\head
  {http://dickwyn.xyz/}
  {Dick Wyn Yong}
  {dickwyn@outlook.com}
  {+1 (480) 388-5741}
  {Github}
  {https://github.com/dickwyn}
  {dickwyn}
  {LinkedIn}
  {https://www.linkedin.com/in/dickwyn}

%   SUMMARY   %
\section{Summary}
\sectionStart
  \summaryText
  {Senior Computer Science student with experience in developing full stack web applications using technologies such as JavaScript (ES6), ExpressJS and MongoDB. Seeking a \textbf{Summer 2018 Internship} to leverage exemplary coding skills, analytical skills and leadership skills.}
\sectionEnd

%   EDUCATION   %
\section{Education}
\sectionStart
  \educationItem
    {Bachelor of Science} 
    {Computer Science} 
    {Expected December 2018}
    {Arizona State University [Tempe, AZ]} 
    {3.68/4.0}
\sectionEnd

%   SKILLS   %
\section{Technical Skills}
\sectionStart
  \skillItem
    {Languages}
    {JavaScript (ES6), Java, C\#, SQL, HTML, CSS/Sass, C/C++, Python, Matlab}
  \skillItem
    {Frameworks}
    {Bootstrap, .NET, Node, jQuery, Jekyll, Express, React, Angular}
  \skillItem
    {Tools}
    {Photoshop, Illustrator, Bash, Git, Gulp, WordPress, Axure RP, Amazon AWS, \LaTeX\ }
  \vspace{3pt}
\sectionEnd

%   PROJECTS   %
\section{Projects}
\sectionStart
  \projectHeading
    {http://testorangesafe.dickwyn.xyz/}
    {SafeDevils}
    {(JavaScript, NodeJS, PugJS)}
    {May 2018}
  \listStart
    \bulletItem
      {A simple safety web application that integrates the SafeTrek API to invoke emergency services when the alert button is triggered.}
  \listEnd
  \projectHeading
    {}
    {SFLE Knowledgebase}
    {(AxureRP, MySQL, NodeJS)}
    {February 2018 - Present}
  \listStart
    \bulletItem
      {Prototyped an interactive web application with Axure RP where practitioners and the public can browse the solutions within the database.}
    \bulletItem
      {Designed a scalable open-source database using MySQL that stores data from researchers and stakeholders about sustainable local food economies.}
  \listEnd
  \projectHeading
    {https://goo.gl/EsvFb6}
    {Sound Waves}
    {}
    {January 2017 - April 2017}
  \listStart
    \bulletItem
      {Prototyped a side-scrolling mobile game which included a scoring system, game streaks and a theme for SOUNDS Academy to help underprivileged students practice string instruments.}
    \bulletItem
      {Won EPICS Catalyst Award from Ira A. Fulton Schools of Engineering.}
  \listEnd
  \projectHeading
    {https://github.com/dickwyn/onelap}
    {OneLap}
    {(C, Kinetis Microcontroller)}
    {April 2015 - June 2015}
  \listStart
    \bulletItem
      {Developed an autonomous navigation algorithm in C that aligned the vehicle to the center of two white lines. Model race car built with a FRDM-KL25Z board, a line scan camera and a servo.}
  \listEnd
\sectionEnd
  
%   EXPERIENCE   %
\section{Experience}
\sectionStart
  \jobHeading
    {Teaching Assistant}
    {August 2016 - December 2017}
    {Ira A. Fulton Schools of Engineering [Tempe, AZ]}
  \listStart
    \bulletItem
    {Assisted the professor to guide a class of 40 freshmen students to understand introductory programming techniques.}
    \bulletItem
    {Involved in creating learning modules for students in \textbf{Matlab} to help learn hardware programming on the Lego Mindstorms platform.}
  \listEnd
\sectionEnd

%   LEADERSHIP   %
\section{Leadership}
\sectionStart
  \jobHeading
    {Student Facilitator}
    {February 2017 - Present}
    {ASU Student and Cultural Engagement [Tempe, AZ]}
  \listStart
    \bulletItem
    {Facilitated diversity \& inclusion workshops for 80 students on topics such as conflict resolution, cultural adjustment and intersectionality of sex, gender \& sexuality.}
  \listEnd
  \jobHeading
    {Vice President}
    {September 2017 - April 2018}
    {ASU Coalition of International Students [Tempe, AZ]}
  \listStart
    \bulletItem
    {Coordinated 58 student leaders within the coalition to host 5 large-scale events that celebrated culture from all around the world that collectively engaged over 6,000 students throughout the academic year.}
    \bulletItem
    {Supervised all internal operations within the coalition such as project management and conducting strategic reviews.}
  \listEnd
\sectionEnd

\end{document}